\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-11-06 src/chain.tex
camera ready ?

\section{Fault Tolerance}
In this section we consider the problem of a service chain placement when there 
is also demand for fault tolerance.
Formally, given a physical network, a virtual specification and a parameter 
$\phi \in \mathbb{N}$, a $\phi$-robust placement is a collection of $\phi$ placements,
$f_1,\ldots,f_\phi$,
that correspond to $\phi$ internal vertex disjoint physical paths. 
We are looking for a $\phi$-robust placement that minimize the total cost:
$$
\sum_{i = 1}^\phi \sum_j c(\alpha_j,f_i(\alpha_j))
$$

>>>>

\paragraph{\textbf{FPT Algorithm}}
Let $k = |N|$, we present an FPT algorithm that runs in $k!$ iterations and is
guaranteed to find the optimal placement.
For each possible permutation of the $k!$ permutations on the $k$ neighborly vertices, 
the algorithm applies the graph orientation procedure as described above,
and then executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}, 
thus the running time of the algorithm is $O(k!(A + O))$ where $A$ is the running time of the
FPTAS and $O$ is the time it takes to orient an undirected graph.

\begin{theorem}
There is an FPT algorithm that finds a $(1+\eps)$-approximate placement 
in $O(k!(A + O))$ time
\end{theorem}

\begin{proof}
The running time of the algorithm follows from the discussion above, the correctness of the 
algorithm follows directly from the fact that there is a correct orientation among the $k!$
possible once that corresponds to the optimal placement 
\qed
\end{proof}
